Output Summary

### 2021-11-24 03-post-process/output-plots.Rmd
Update overwinter surv plotting code to use WUL instead of PEU

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j) {
  # extract parr, scale it to PEU, and create new post object
  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
  Pa_scaled = Pa/jags_data$peu[j]
  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))

@@

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

>>>>

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j) {
  # extract parr, scale it to WUL, and create new post object
  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
  Pa_scaled = Pa/jags_data$wul[j]
  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))

@@

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/WUL", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```
